Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s}$ =13 TeV

### 2020-05-26 paper.tex
section 3 updated
section 3 and 4 updated

\begin{abstract}
\input{abstract.tex}
\end{abstract}
\end{titlepage}
\setcounter{page}{2}

>>>>

\begin{abstract}
%\input{abstract.tex}

%In recent years, similar features between small systems like proton-proton (pp) collisions and large systems like lead-lead collisions have been observed via long-range correlations in pseudorapidity (so-called the ridge) for pairs of charged hadrons. Many theoretical approaches have been applied to interpret the similarity. However, it is still controversial whether the ridge in small systems is originated from initial or final-state effects of the collision.

To further investigate the ridge effect in small systems, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV. The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016 because of increased statistics for high-multiplicity pp collisions.  The results are compared to previous measurements by other LHC experiments. In addition, we explore possible physical origins of the ridge effects in small systems by studying the results as a function of the energy scale of the hard fragmentation process and comparing the various theoretical models tuned for the initial and final state effect.
\end{abstract}

\end{titlepage}

\setcounter{page}{2}

### 2020-05-26 sec_ana.tex
section 3 and 4 updated

\section{Systematic Uncertainty}
\label{sec:uncertainties}
The systematic uncertainty is evaluated by varying the event selection, track selection, yield extraction procedures and detector efficiency correction. Each source is assumed uncorrelated. The uncertainty from the event selection can be divided into Pile-up rejection and primary vertex selection. The uncertainty from the track selection is estimated by changing the selection criteria. The uncertainty from the yield extraction procedures can be divided into long-range definition and ZYAM procedure. The uncertainty from the efficiency correction is estimated by enlarging the event mixing bins, which is relevant to acceptance correction. Finally, The uncertainty from the application of track efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed by true particles. The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ is summarized by averaging the each uncertainty for a given $\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}}$. The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ or $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ is summarized by averaging the each uncertainty for a given $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection.
\begin{table}[!h]
\caption{ The relative systematic uncertainty of the associated yield spectrum as function of 
$(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ (second), $\it{p}_{\rm{T,Lead}}$ (thrid) or $\it{p}_{\rm{T,jet}}$ (fourth) selection in high multiplicity (0--0.1\%) }
\centering
\begin{tabular}{|c|<{\centering}m{8em}|<{\centering}m{6em}|<{\centering}m{6em}|}
\hline 
Sources & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
Pileup cut			& $\sim$0.8	&0-4		&0-4		\\ \hline
Primary Vertex		& $\sim$2.4	&1-12	&1-8		\\ \hline

@@

The uncertainty from the pileup rejection is estimated by inspecting the changes of results with different rejection methodologies from the default one. The estimated uncertainty is 1\% without $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection. The uncertainty is increased up to 4\% with $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection.

The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_{vtx}|<$ 8 cm to $|z_{vtx}|<$ 6 cm. The narrower primary vertex selection allows one to accept more forward tracks, which could be very sensitive to select long-range side. The estimated uncertainty is increased up to 12\% from 1\%, which is obtained without the event scale selection.

The uncertainty from the track selection is estimated by varying the track selection methodologies from the one optimized for refining the angular track distribution to the other optimized for particle identification. The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/\it{c}\rm{} tracks.

The uncertainty from the ZYAM procedure is estimated by varying the finding-scope for minimum position. The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/\it{c}\rm{} tracks, which is not largely affected by the event scale selection.

The uncertainty from the long $\Delta\eta$ range is estimated by varying the $\Delta\eta$ range. The uncertainty might include effects from the longitudinal de-correlations and possible non-flow contamination, which is thought be small. The estimated uncertainty is increased up to 9\% from 3\%, which is obtained by averaging the whole transverse momentum range.

The uncertainty from the mixing pool bin size of primary vertex is estimated by varying the bin size from 2.0 cm to 1.0 cm. The estimated uncertainty is 1-16\%

*The M.C. closure test for efficiency correction results in $\sim$2.5\% discrepancy. The discrepancy is considered into systematic uncertainty.

>>>>

\section{Systematic Uncertainty}
\label{sec:uncertainties}
The systematic uncertainty is evaluated by varying the event selection, track selection, yield extraction procedures and detector efficiency correction. Each source is assumed uncorrelated. The uncertainty from the event selection can be divided into pile-up rejection and primary vertex selection. The uncertainty from the track selection is estimated by changing the selection criteria. The uncertainty from the yield extraction procedures can be categorized into long-range definition and ZYAM procedure. The uncertainty from the efficiency correction is estimated by enlarging the event mixing bins, which is relevant to the acceptance correction. Finally, The uncertainty from the application of the detector efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed. The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ is summarized by averaging each uncertainty for given $\it{p}_{\rm{T, trig}}$ and $\it{p}_{\rm{T, assoc}}$. The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ and $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ is summarized by averaging the each uncertainty for a given $\it{p}_{\rm{T, Lead}}$ and $\it{p}_{\rm{T, Jet}}$ selection, respectively.
\begin{table}[!h]
\caption{ The relative systematic uncertainty of the associated yield spectrum as function of 
$(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ (second), $\it{p}_{\rm{T,Lead}}$ (thrid) or $\it{p}_{\rm{T,jet}}$ (fourth) selection in high multiplicity (0--0.1\%) }
\centering
\begin{tabular}{|c|<{\centering}m{8em}|<{\centering}m{6em}|<{\centering}m{6em}|}
\hline 
Sources & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
Pileup cut			& $\sim$0.8	&0-4		&0-4		\\ \hline
Primary Vertex		& $\sim$2.4	&1-12	&1-8		\\ \hline

@@

The uncertainty from the pileup rejection is estimated by measuring the changes of results with different rejection criteria from the default one. The estimated uncertainty is 1\% without $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection. The uncertainty is increased up to 4\% with $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection. The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_{vtx}|<$ 8 cm to $|z_{vtx}|<$ 6 cm. The narrower primary vertex selection allows one to accept more forward tracks, which could be very sensitive to select long-range side. The estimated uncertainty is increased up to 12\% from 1\%, which is obtained without the event scale selection. The uncertainty from the track selection is estimated by varying the track selection criteria from the one optimized for refining the angular track distribution to the other optimized for particle identification. The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/\it{c}\rm{} tracks.

The uncertainty from the ZYAM procedure is estimated by varying the finding-scope for minimum position. The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/\it{c}\rm{} tracks, which is not largely affected by the event scale selection. The uncertainty from the long $\Delta\eta$ range is estimated by varying the $\Delta\eta$ range. The uncertainty might include effects from the longitudinal de-correlations and possible non-flow contamination, which is thought be small. The estimated uncertainty is increased up to 9\% from 3\%, which is obtained by averaging the whole transverse momentum range.
The uncertainty from the mixing pool bin size of primary vertex is estimated by varying the bin size from 2.0 cm to 1.0 cm. The estimated uncertainty is 1-16\%

%*The M.C. closure test for efficiency correction results in $\sim$2.5\% discrepancy. The discrepancy is considered into systematic uncertainty.
